YouTube Kids: The Effect of YouTube on Children’s Racial Learning

### 2025-04-14 manuscript.qmd
Updated manuscript draft

---
title: "YouTube Kids: The Effect of YouTube on Children’s Racial Learning"
shorttitle: "YouTube Racial Attitudes"
author: 
- name: Reilly Amera
  corresponding: true
  email: ramera@uchicago.edu
  affiliations:
  - id: id1
    name: "University of Chicago"
    department: MA Program in the Social Sciences
    address: "1155 E 60th St."
    city: Chicago
    region: IL
    country: USA
    postal-code: 60637
abstract: "One way in which children learn about group dynamics within their racial world is from patterns in their daily environments. The current study seeks to understand the degree to which YouTube, a popular form of social media, exposes children to negatively valenced racial patterns, and potentially affects their beliefs. Dyads of parents and 8-13 year-old children (N = 18) describe daily YouTube usage, and the effects of children's YouTube usage are assessed. In the present sample, there is no relationship between children's YouTube usage, racial patterns they may observe, and negative racial beliefs."
floatsintext: true
numbered-lines: false
bibliography: [r-references.bib, bibliography.bib]
link-citations: true
draft-date: false
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  email: "Email"
format:
  apaquarto-html: default
  apaquarto-docx: default
  apaquarto-typst: 
    keep-typ: true
    list-of-figures: true
    list-of-tables: true
    toc: true
  apaquarto-pdf:
    documentmode: man
    keep-tex: true
    list-of-figures: true
    list-of-tables: true
editor: visual
---

@@

# Necessary libraries
#install.packages(papaja)
library(papaja)
#install.packages(kableExtra)
library(kableExtra)
#install.packages(psych)
library(psych)
library(knitr)
library(broom)
library(tidyverse)

@@

# read in data
youtube <- read_csv("data/youtube.csv", col_names = TRUE)

@@

Is YouTube making kids more racist? Despite sounding like the cultural fear-mongering often associated with screen time and development, such a question refers to real concerns that psychological research has yet to address: what are children really learning from YouTube, particularly with regard to race?

@@

This study will examine the relationship between YouTube usage and children’s development of racial attitudes, so as to understand whether and the degree to which YouTube may be a site of ethnic-racial socialization where children develop prejudices against those of other races.

I hypothesize that time spent on YouTube and children’s observation of racial regularities should covary; as children spend more time on YouTube, they may observe more negatively valenced racial regularities including people of color [@guoharlow_2014_usergenerated; @rollinsetal_2022_who]. Thus, I hypothesize that if children spend more time on YouTube, they will display greater racial stereotyping and prejudice against outgroups. While some children may not be consciously aware of on-screen racial regularities, these dynamics may still affect their racial attitudes [@hugheswatford_2022_racial]. As such, I hypothesize that the relationship between children’s time spent on YouTube and their exhibited racial stereotyping and prejudice will be mediated by their observations of negative racial regularities.

One additional factor that may moderate the relationship between time spent on YouTube and racial attitudes is whether a child’s favorite YouTuber is of a race other than their own, via the parasocial contact hypothesis. This theory suggests that when individuals have limited real life interpersonal contact with minority groups, the formation of parasocial (one-sided) relationships with outgroup media figures may reduce stereotyping and prejudice [@schiappaetal_2005_parasocial; @wongetal_2022_theorizing]. Much of the parasocial contact hypothesis literature explores the prejudice reduction made possible by parasocial relationships with television characters, yet the growing popularity of social media presents another medium through which parasocial relationships may be formed. If positive parasocial contact hypothesis effects may be observed when individuals form relationships with characters in other media, so too should these effects be observed when individuals have parasocial relationships with outgroup influencers [@banasetal_2020_metaanalysis]. Thus, I pose my third hypothesis: the relationship between the amount of time that children spend on YouTube and their racial stereotyping and prejudice will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own. Specifically, if children have a favorite YouTuber of a race other than their own and they have a parasocial relationship with this YouTuber, they will display less racial stereotyping and prejudice.

@@

This study includes dyads of parents and children between the ages of 8 and 13 [^1]. Though children may express negative racial attitudes prior to this point in development, during early adolescence, children develop the ability to recognize and reflect on the racial patterns and dynamics present in their environments [@hugheswatford_2022_racial]. As such, this age range allows me to observe how the observation racial regularities present on YouTube may affect children’s stereotyping and prejudicial attitudes, and how such a phenomenon develops. Participants were recruited through Qualtrics Panels, allowing me to obtain a representative sample of parents and children; other studies have used Qualtrics Panels with similar methods and populations [@byrdahn_2020_profiles].

[^1]: Pilot data has demonstrated that Qualtrics Panels has not, thus far, been as stringent in participant age verification. As such, data used presently is from a broader age range than will be included in the final sample, after stricter age validation has been included.

Pilot data has been collected in March of 2025 from families recruited via Qualtrics Panels (*N* = `r length(youtube$transaction_id)`). Participating families receive two Qualtrics surveys to be completed asynchronously, and receive compensation (as determined by Qualtrics Panels) after both surveys have been completed. First, parents complete a demographics and YouTube usage survey, then children complete their own survey.

@@

In the parent survey, participants answer questions related to parent and child demographics (child age, race/ethnicity, parent income and level of education, etc.), as well as questions regarding their child’s YouTube usage (for instance, time spent on YouTube, as reported by their child’s device screen time).

In the child survey, children answer questions related to their YouTube usage, such as time spent on YouTube and their favorite genre. Next, they will either answer more questions pertaining to YouTube content, or their general racial attitudes; either block of questions will appear randomly, so as to reduce the influence of question order. In the racial attitudes section, children will answer questions regarding outgroup prejudices, as rated on a Likert scale. They will also complete one friend choice item, as a simple exploratory measure of racial preference. In the YouTube content section, children will be asked to think of their favorite YouTuber as they answer questions related to whether they have a parasocial relationship with that YouTuber, as well as their observations of racial regularities on YouTube.

The particular measures used in the child survey are as follows:

1. Beliefs about groups (adapted from @halperinetal_2012_promoting)
2. Perceived homophily in behavior and appearance (adapted from @mccroskeyetal_1975_development)
3. Parasocial interaction with a YouTuber (adapted from @sungetal_2023_shes)
4. Racial regularities (created based on @rollinsetal_2022_who)
5. Friend choice (adapted from @amemiyabian_2024_why)

@@

Beliefs about groups, particularly in terms of group malleability, were chosen as the primary outcome measure to assess racial attitudes. Such questions, adapted from @halperinetal_2012_promoting, address whether children have fixed or malleable views regarding outgroups (e.g. when prompted to think about groups with different skin colors than their own, children are asked the extent to which they agree with the statement, "These groups of people can't really change the way they act"). Higher scores in this domain demonstrate more fixed evaluations of outgroup members, suggesting an underlying racial essentialism, or a belief in the intrinsic nature of racial difference [@waxman_2021_racial].

Composite scores have been created for each measure. All analyses have been completed in RStudio [@R-base], primarily within the tidyverse and psych packages (@R-tidyverse; @R-psych).

@@

Looking first to the distributions of time spent on YouTube among  participants, just as many children use YouTube every day as (*N* = `r sum(youtube$daily == 'Every Day')`) as those who do not (*N* = `r sum(youtube$daily == 'Not Every Day')`). And, as shown in @fig-time-distribution, children who use YouTube every day appear to use YouTube for more time on an average day than children who do not. On average, parents report that children spend about `r round(mean(youtube$Ptime), digits = 0)` minutes, or `r round(mean(youtube$Ptime)/60, digits = 0)` hour, on YouTube on an average day. Some children, as parents report, watch as much as `r round(max(youtube$Ptime)/60, digits = 0)` hours of YouTube, while others watch only `r round(min(youtube$Ptime)/60, digits = 0)`. Children's self-report YouTube usage reflects a similar pattern, as shown in @tbl-frequency: the majority of participants report watching YouTube for 30 minutes to 1 hour each day.

```{r}
#| label: fig-time-distribution
#| fig-cap: "Distribution of participants' YouTube watch time"
#| fig-width: 6
#| fig-height: 4

ggplot(subset(youtube, !is.na(Ctime)), aes(x = Ctime)) + 
  geom_bar(color = "black", fill = "grey") +
  facet_grid(~ daily) +
  scale_x_discrete(labels = c("About 15 minutes a day" = "~ 15 min", "About 30 minutes a day" = "~ 30 min", "About 45 minutes a day" = "~ 45 min", "About 1 hour a day" = "~ 1 hr", "About 1 and 1/2 hours a day" = "~ 1.5 hr", "More than 2 hours a day" = "> 2 hr")) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  labs(x = "Time Spent on YouTube (Self-Reported)",
       y = "Number of Participants",
       title = "Time Spent on YouTube on an Average Day",
       subtitle = "Comparing children who use YouTube every day and children who do not") +
  my_theme()

@@

```{r}
#| label: generate-frequency-table

frequency <- round(addmargins(prop.table(table(youtube$Ctime, youtube$daily))), 2)
```

```{r}
#| label: tbl-frequency
#| tbl-cap: "YouTube Screen Time Frequency Table"

kable(frequency, 
      align = c("c", "c", "c"),
      # Setting caption here
      caption = "Proportions of watch times in children who watch YouTube every day vs those who do not") %>% 
  kable_styling(position = "center", latex_options = c("striped"))
```

```{r}
#| label: anova-outputs

# ANOVA: racial regularities score predicted by time spent on YT (categorical self-report)
aov_reg_ctime <- aov(regularity_score ~ Ctime, data = youtube)

# ANOVA: racial regularities score predicted by perceptions of how often kids see outgroup (categorical)
aov_reg_outfreq <- aov(regularity_score ~ outgroup_freq, data = youtube)

# ANOVA: racial regularities score predicted by perceptions of how often kids see outgroup (categorical)
aov_mall_outfreq <- aov(malleable_score ~ outgroup_freq, data = youtube)
```

@@

Preliminary one-way analysis of variance does not indicate that greater amounts of time spent on YouTube (self-report) is associated with a higher racial regularities score (`r report_anova(aov_reg_ctime)`). Similarly, thus far, one-way analysis of variance does not indicate that there is any association between ratings of frequency with which children encounter those of other racial groups and racial regularities scores, (`r report_anova(aov_reg_outfreq)`). Further, one-way analysis of variance does not indicate a significant relationship between the primary racial attitudes outcome measure, group malleability, and frequency of seeing racial outgroups on YouTube, (`r report_anova(aov_mall_outfreq)`).

```{r}
#| label: regression-models

# Regressing malleability against time spent on YouTube (reported by parents)
lm_mt <- lm(malleable_score ~ Ptime, data = youtube)

# Regressing malleability against time spent on YouTube (reported by parents) and whether or not YouTube is used daily
lm_mtd <- lm(malleable_score ~ Ptime + daily, data = youtube)

# Regressing malleability against regularity
lm_mr <- lm(malleable_score ~ regularity_score, data = youtube)
```

```{r}
#| label: regression-report-functions

# Taken from apaquarto demo

# report_regression takes a lm model object as an argument
# Returns string of format: "$F$(df, df.residual) = F-value, $p$ = p-value"

report_regression <- function(model) {

  # Extract coefficients and p-values
  m_glance <- glance(model)
  # Format the p-value
  p_value <- apa_p(m_glance$p.value, add_equals = TRUE)
  # Create a string with the results
  report <- paste0("$F$(", 
                   m_glance$df, 
                   ", ", m_glance$df.residual, 
                   ") = ", round(m_glance$statistic, 2), 
                   ", $p$ ", p_value)
  # Return report
  return(report)    
}
```

Regressing malleability scores against parent reports of time spent on YouTube, no significant relationship is observed (`r report_regression(lm_mt)`). . This relationship remains unchanged and similarly insignificant when daily use is added as a predictor (`r report_regression(lm_mtd)`). Such relationships, as well as that of regularity score and YouTube usage, may be observed in @fig-malleable and @fig-regularity. Based on pilot sample alone, there is not enough data to conduct analyses with regard to the effect of YouTuber on racial attitudes, but the modal favorite YouTuber reported has thus far been `r mode(youtube$favorite)` (*N* = `r sum(youtube$favorite == 'MrBeast')`). Preliminary relationships between favorite YouTuber (this YouTuber in particular) as well as malleability and regularity scores may be found in @fig-malleable and @fig-regularity respectively.

```{r}
#| label: fig-malleable
#| fig-cap: "Correlations Between Time Spent On YouTube and Group Malleability Beliefs"
#| fig-width: 5
#| fig-height: 2

ggplot(data = youtube %>% 
         # filtering outliers that are too low
             filter(Ptime > 10)) +
  aes(x = Ptime, y = malleable_score) +
  facet_grid(~ daily, scales = "free_x") +
  stat_smooth(method = "lm", color = "#800000") +
  geom_point(aes(shape = youtuber)) +
  scale_shape_manual(values = c("Not MrBeast" = 16, "MrBeast" = 1)) +
  labs(x = "Time Spent on YouTube (minutes)", y = "Malleability Score",
       shape = "Favorite YouTuber",
       title = "Malleability and Time Spent on YouTube",
       caption = "Note: MrBeast is the modal favorite YouTuber.") +
  my_theme()
```

```{r}
#| label: fig-regularity
#| fig-cap: "Correlations Between Time Spent On YouTube and Racial Regularities"
#| fig-width: 5
#| fig-height: 2

ggplot(data = youtube %>% 
         # filtering outliers that are too low
             filter(Ptime > 10)) +
  aes(x = Ptime, y = regularity_score) +
  facet_grid(~ daily, scales = "free_x") +
  stat_smooth(method = "lm", color = "#800000") +
  geom_point(aes(shape = youtuber)) +
  scale_shape_manual(values = c("Not MrBeast" = 16, "MrBeast" = 1)) +
  labs(x = "Time Spent on YouTube (minutes)", y = "Regularity Score",
       shape = "Favorite YouTuber",
       title = "Racial Regularities and Time Spent on YouTube",
       caption = "Note: MrBeast is the modal favorite YouTuber.") +
  my_theme()
```

>>>>

---
title: "YouTube Kids: The Effect of YouTube on Children’s Racial Learning"
shorttitle: "YouTube Racial Attitudes"
author: 
- name: Reilly Amera
  corresponding: true
  email: ramera@uchicago.edu
  affiliations:
  - id: id1
    name: "University of Chicago"
    department: MA Program in the Social Sciences
    address: "1155 E 60th St."
    city: Chicago
    region: IL
    country: USA
    postal-code: 60637
abstract: "To what extent might YouTube influence children’s beliefs about racial outgroups? Though it is well established that children can learn about group dynamics within their racial world from patterns in their daily environments, the majority of research in this domain has focused on in-person environmental dynamics. The current study examines whether YouTube exposes children to negative outgroup behaviors, potentially affecting their beliefs. In an online questionnaire, dyads of parents and 8-13 year-old children (N = 200 dyads) described children’s daily YouTube usage. We found that time spent on YouTube each week was not associated with increased perception of negative racial patterns on YouTube (B = 0.00, p = .397), nor was time spent on YouTube associated with an increase in prejudice against racial outgroups (B = 0.00, p = .376). However, male participants (t = -2.45, p = .029) and participants with higher parasociality scores (B = 0.81, SE = 0.08, p < .001) displayed greater prejudice. These findings suggest that prejudice is predicted by more than just online exposure to negative racial patterns; children’s identities and preferences may play a larger role."
floatsintext: true
numbered-lines: false
bibliography: [r-references.bib, bibliography.bib]
link-citations: true
draft-date: false
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  email: "Email"
format:
  apaquarto-html: default
  apaquarto-docx: default
  apaquarto-typst: 
    keep-typ: true
    list-of-figures: true
    list-of-tables: true
    toc: true
  apaquarto-pdf:
    documentmode: man
    keep-tex: true
    list-of-figures: true
    list-of-tables: true
    toc: true
editor: visual
---

@@

# Necessary libraries
library(papaja)
library(lm.beta)
library(citr)
library(mediation)
library(kableExtra)
library(psych)
library(knitr)
library(broom)
library(tidyverse)

# R References
# r_refs(file = "r-references.bib")

@@

# read in data
youtube <- read_csv("data/youtube.csv", col_names = TRUE)
favorite_youtuber <- read_csv("data/favorite_youtuber.csv", col_names = TRUE)
```

@@

Is YouTube making children more racist? Despite sounding like the cultural fear-mongering often associated with screen time and development, such a question refers to real concerns that psychological research has yet to address: what are children really learning from YouTube, particularly with regard to race?

@@

This study will examine the relationship between YouTube usage and children’s development of racial attitudes, so as to understand whether and the degree to which YouTube may be a site of ethnic-racial socialization where children develop stereotypes regarding those of other races.

I hypothesize that time spent on YouTube and children’s observation of racial regularities should covary; as children spend more time on YouTube, they may observe more negatively valenced, stereotypical racial regularities including people of color [@guoharlow_2014_usergenerated; @rollinsetal_2022_who]. Thus, I hypothesize that if children spend more time on YouTube, they will display more fixed beliefs regarding racial outgroups. While some children may not be consciously aware of on-screen racial regularities, these dynamics may still affect their racial attitudes [@hugheswatford_2022_racial]. As such, I hypothesize that the relationship between children’s time spent on YouTube and their exhibited racial stereotyping will be mediated by their observations of negative racial regularities.

One additional factor that may moderate the relationship between time spent on YouTube and racial attitudes is whether a child’s favorite YouTuber is of a race other than their own, via the parasocial contact hypothesis. This theory suggests that when individuals have limited real life interpersonal contact with minority groups, the formation of parasocial (one-sided) relationships with outgroup media figures may reduce stereotyping and prejudice [@schiappaetal_2005_parasocial; @wongetal_2022_theorizing]. Much of the parasocial contact hypothesis literature explores the prejudice and stereotype reduction made possible by parasocial relationships with television characters, yet the growing popularity of social media presents another medium through which parasocial relationships may be formed. If positive parasocial contact hypothesis effects may be observed when individuals form relationships with characters in other media, so too should these effects be observed when individuals have parasocial relationships with outgroup influencers [@banasetal_2020_metaanalysis]. Thus, I pose my final hypothesis: the relationship between the amount of time that children spend on YouTube and their racial stereotyping will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own. Specifically, if children have a favorite YouTuber of a race other than their own and they have a parasocial relationship with this YouTuber, they will display less racial stereotyping.

@@

This study includes dyads of parents and children between the ages of 8 and 13 years old. Though children may express negative racial attitudes prior to this point in development, during early adolescence, children develop the ability to recognize and reflect on the racial patterns and dynamics present in their environments [@hugheswatford_2022_racial]. As such, this age range allows me to observe how the observation racial regularities present on YouTube may affect children’s stereotyping and prejudicial attitudes, and how such a phenomenon develops. Participants were recruited through Qualtrics Panels, allowing me to obtain a representative sample of parents and children; other studies have used Qualtrics Panels with similar methods and populations [@byrdahn_2020_profiles].

Data was been collected in March of 2025 from families recruited via Qualtrics Panels. `r length(youtube$transaction_id)` dyads were collected; the final sample contained `r length(youtube$transaction_id)` parents and `r length(youtube$transaction_id)` children (*M* = `r round(mean(youtube$age), digits = 1)`, `r sum(youtube$gender == "female")` girls). Participating families receive two Qualtrics surveys to be completed asynchronously, and receive compensation (as determined by Qualtrics Panels) after both surveys have been completed. First, parents complete a demographics and YouTube usage survey, then children complete their own survey.

@@

In the parent survey, participants answered questions related to parent and child demographics (child age, race/ethnicity, parent income and level of education, etc.), as well as questions regarding their child’s YouTube usage (for instance, time spent on YouTube on an average day).

In the child survey, children answered questions related to their YouTube usage, such as time spent on YouTube and their favorite genre. Next, they either answered more questions pertaining to YouTube content, or their general racial attitudes; either block of questions appeared randomly, so as to reduce order effects. In the racial attitudes section, children answered questions regarding outgroup prejudices, as rated on a Likert scale (all coded such that 1 = *Really disagree* and 5 = *Really agree*). They also completed one friend choice item, as a measure of racial preference. In the YouTube content section, children were asked to think of their favorite YouTuber as they answered questions related to whether they have a parasocial relationship with that YouTuber, as well as their observations of racial regularities on YouTube, as rated on the same Likert scale as in previous questions.

Beliefs about groups, particularly in terms of group malleability, were chosen as the primary outcome measure to assess racial attitudes, stereotyping in particular. Such questions, adapted from @halperinetal_2012_promoting, address whether children have fixed or malleable views—stereotypes—regarding outgroups (e.g. when prompted to think about groups with different skin colors than their own, children are asked the extent to which they agree with the statement, "These groups of people can't really change the way they act"). Higher scores in this domain demonstrate more fixed evaluations of outgroup members, suggesting an underlying racial essentialism, or a belief in the intrinsic nature of racial difference [@waxman_2021_racial].

Time spent on YouTube, reported by parents, is the primary predictor of racial attitudes. Parents reported the amount of days their child spends on YouTube in an average week, as well as the amount of time their child spends on YouTube in an average day. These answers were combined to create an hours per week score.

Racial regularities, hypothesized to mediate the relationship between time spent on YouTube and children's racial attitudes, were measured using racial regularities questionnaire items created for this study. As racial regularities are defined in terms of consistent and repeated racialized patterns in a particular environment [@hugheswatford_2022_racial],  this measure was designed to capture potential behavioral patterns in racial outgroups that may appear on YouTube. This measure was created using patterns in YouTube videos as captured in a large-scale content analysis by @rollinsetal_2022_who, and included both positive and negative behaviors. Children were asked whether they agreed that people who did not look like them expressed each behavior.

Children's parasocial relationships with YouTubers, a potential moderator in the relationship between time spent on YouTube and negative racial attitudes, was measured using a composite score of two questionnaires: perceived homophily in behavior and appearance (adapted from @mccroskeyetal_1975_development) and parasocial interaction with a YouTuber (adapted from @sungetal_2023_shes). After listing and being prompted to think about their favorite YouTuber, in these questionnaires, children indicated the degree to which their favorite YouTuber looks, acts, and thinks like them, as well as whether this YouTuber could be their friend. Children also completed a friend choice measure, adapted from @amemiyabian_2024_why; this measure captures children's explicit racial preferences with regard to peers.

@@

@@

## Regularities, Attitudes, and Time Spent on YouTube {#sec-h1-3}

```{r}
#| label: report-correlation

report_cor <- function(result) {
  r <- round(result$estimate, 2)
  p <- ifelse(result$p.value < .001, "< .001", paste0("= ", round(result$p.value, 3)))
  ci <- round(result$conf.int, 2)

  paste0("r = ", r, ", 95% CI [", ci[1], ", ", ci[2], "], p ", p)
}
```

```{r}
#| label: correlation-time-reg

cor_tr <- cor.test(youtube$Ptime_max_score, youtube$regularity_score)  
```

```{r}
#| label: regression-report-function

# report regression function
report_regression <- function(model) {

  # Extract coefficients and p-values
  m_glance <- glance(model)
  # Format the p-value
  p_value <- apa_p(m_glance$p.value, add_equals = TRUE)
  # Create a string with the results
  report <- paste0("$F$(", 
                   m_glance$df, 
                   ", ", m_glance$df.residual, 
                   ") = ", round(m_glance$statistic, 2), 
                   ", $p$ ", p_value,
                   ", $R^2$ = ", round(m_glance$r.squared, 2))
  # Return report
  return(report)    
}
```

```{r}
#| label: h1-regressions

# Regressing malleability against time, controlling for regularities and age
h1 <- lm(malleable_score ~ Ptime_max_score + regularity_score + age + gender, data = youtube)

# Regressing regularities against time, controlling for age
h1.1 <- lm(regularity_score ~ Ptime_max_score + age + gender, data = youtube)
```

```{r}
#| label: report-oneway-ttest

report_onesample <- function(t_result) {
  t_val <- round(t_result$statistic, 2)
  df <- round(t_result$parameter, 0)
  p_val <- t_result$p.value
  p_str <- ifelse(p_val < .001, "< .001", paste0("= ", sub("^0+", "", format(round(p_val, 3), nsmall = 3))))
  ci <- round(t_result$conf.int, 2)
  mean_val <- round(t_result$estimate, 2)

  paste0("*t*(", df, ") = ", t_val, ", *p* ", p_str,
         ", 95% CI [", ci[1], ", ", ci[2], "], *M* = ", mean_val)
}

@@

```{r}
#| label: onesample-ttest

# One way t-test of mean regularity score against a neutral average
onesample <- t.test(youtube$regularity_score, mu = 0.5)
```

```{r}
#| label: report-mlr-results

report_mlr_coefficients <- function(model, predictors) {
  # Compute standardized coefficients
  standardized_model <- lm.beta::lm.beta(model)
  betas <- coef(standardized_model)
  p_vals <- summary(model)$coefficients[, "Pr(>|t|)"]

  # Clean names (remove backticks, spaces)
  names(betas) <- gsub("`", "", names(betas))
  names(p_vals) <- gsub("`", "", names(p_vals))

  # Build APA-style strings
  apa_results <- sapply(predictors, function(pred) {
    beta <- round(betas[pred], 2)
    p <- p_vals[pred]
    p_formatted <- ifelse(p < .001, "< .001", paste0("= ", sub("^0+", "", format(round(p, 3), nsmall = 3))))
    paste0("*β* = ", beta, ", *p* ", p_formatted)
  })

  names(apa_results) <- predictors
  return(apa_results)
}

To test my first hypothesis that increased time spent on YouTube should generally covary with children's observations of negative racial regularities, I calculated the correlation between children's time spent on YouTube per week and racial regularities scores. Time spent on YouTube was not significantly correlated with children's perceptions of racial regularities (`r report_cor(cor_tr)`). This lack of relationship was confirmed by regressing regularity scores on time (`r report_regression(h1.1)`); though the overall model is significant, time is not a significant predictor of children's observations of racial regularities (`r report_mlr_coefficients(h1.1, "Ptime_max_score")`). The significance of this model comes from the addition of gender (`r report_mlr_coefficients(h1.1, "genderMale")`), added as a control alongside age (`r report_mlr_coefficients(h1.1, "age")`). Such controls were added so as to curtail variance, as well as to account for age and gender as potential confounds. In the current sample, time spent on YouTube was not correlated nor predictive of children's observation of racial regularities. In general, children's observations of racial regularities in YouTube videos were not significantly different from a neutral reference point (`r report_onesample(onesample)`), and there was much variance in scores overall, as shown in @fig-regularities. However, some of this variance may be explained by children's gender, whether in terms of gendered usage or content.

```{r}
#| label: fig-regularities
#| fig-width: 6
#| fig-height: 4 
#| fig-cap: "Relationship between children's per-week YouTube watching and observation of racial regularities"

ggplot(data = youtube) +
  aes(x = Ptime_max_score, y = regularity_score) +
  geom_point() +
  stat_smooth(method = "lm", color = "#800000", alpha = 0.3) +
  scale_y_continuous(breaks = seq(from = 0, to = 1, by = 0.2)) +
  labs(
    x = "Time Spent on YouTube Per Week (Hours)",
    y = "Observation of Racial Regularities",
    title = "Time Spent on YouTube and Racial Regularities"
  ) +
  my_theme()
```

It was also hypothesized that as a result of the relationship between time spent on YouTube and racial regularities, children who spend greater time on YouTube will display more negative racial attitudes toward outgroups. Regressing racial attitudes against time spent on YouTube, controlling for regularities, age, and gender, time spent on YouTube significantly predicts more fixed racial attitudes (`r report_regression(h1)`). However, despite a significant positive association, the effect size of time alone on racial attitudes was low (`r report_mlr_coefficients(h1, "Ptime_max_score")`). Racial regularity scores significantly predicted racial attitudes: increases in racial regularity scores were significantly associated with increases in fixedness of racial attitudes (`r report_mlr_coefficients(h1, "regularity_score")`), as shown in @fig-reg-mall-regression. As such, though there was no observed relationship between time spent on YouTube and racial regularities, nor did the average participant observe significantly negative racial regularities, racial regularities on YouTube may still play a role in children's racial attitudes. Neither age nor gender were significant in this model.

```{r}
#| label: fig-reg-mall-regression
#| fig-width: 6
#| fig-height: 4 
#| fig-cap: "Correlation Between Racial Regularities Score and Racial Attitudes Score"

ggplot(youtube) +
  aes(x = regularity_score, y = malleable_score) +
  stat_smooth(method = "lm", color = "#800000", linewidth = 0.8, fill = "lightgrey") +
  geom_point() +
  labs(x = "Observation of Negative Regularities", y = "Fixedness in Racial Attitudes",
       title = "Attitudes vs. Regularity Scores") +
  my_theme()
```

```{r}
#| label: report-twosample-ttest

report_twosample <- function(model) {
  # Extract test-statistic and p-value
  t_glance <- glance(model)
  # Format the p-value
  p_value <- apa_p(t_glance$p.value, add_equals = TRUE)
  # Create a string with the results
  report <- paste0("$t$ = ", round(t_glance$statistic, 2), 
                   ", $p$ ", p_value)
  return(report)}
```

```{r}
#| label: gender-effects-ttests

# two sample t tests where H0: μ1 = μ2
reg_twosample <- t.test(regularity_score ~ gender, data = youtube)
mall_twosample <- t.test(malleable_score ~ gender, data = youtube)

# two sample t tests where H0: μ1 > μ2
reg_twosample_alt <- t.test(regularity_score ~ gender, data = youtube, alternative = "less")
mall_twosample_alt <- t.test(malleable_score ~ gender, data = youtube, alternative = "less")
```

Though gender did not significantly predict racial attitudes in the previous model (`r report_mlr_coefficients(h1, "genderMale")`), it did significantly predict children's observations of racial regularities (`r report_mlr_coefficients(h1.1, "genderMale")`). Considering the strength of the correlation between children's observation of racial attitudes on YouTube and their reported racial attitudes, I examined this discrepancy. I conducted two-sample t-tests with racial attitudes and racial regularities: there were significant differences between genders in both reported racial attitudes (`r report_twosample(mall_twosample)`) and racial regularities (`r report_twosample(reg_twosample)`). Further, one-sided t-tests revealed that male participants displayed significantly more fixed racial attitudes than female participants (`r report_twosample(mall_twosample_alt)`) as well as significantly more negative racial regularities (`r report_twosample(reg_twosample_alt)`). As such, it is clear that in this sample, as shown in @fig-reg-mall-regression-gender, gender affects children's expression of more fixed racial attitudes as well as observations of negative racial regularities on YouTube: a child's gender is associated their racial attitudes insofar as gender predicts children's observation of negative racial regularities, which itself then predicts racial attitudes.

```{r}
#| label: fig-reg-mall-regression-gender
#| fig-cap: "Racial attitudes and racial regularity scores, by gender"
#| fig-width: 6
#| fig-height: 4

ggplot(youtube) +
  aes(x = regularity_score, y = malleable_score) +
  facet_wrap(~ gender) +
  stat_smooth(method = "lm", color = "#800000", linewidth = 0.8, fill = "lightgrey") +
  geom_point() +
  labs(x = "Observation of Negative Regularities", y = "Fixedness in Racial Attitudes",
       title = "Attitudes vs. Regularity Scores") +
  my_theme()
```
Finally, turning to the friend choice measure as a gauge of racial attitudes, there were no significant differences between children who chose a friend of the same race/ethnicity as their own and children who did not, in terms of racial attitudes, observations of racial regularities, parasocial relationships with YouTubers, nor choice of favorite YouTuber.

## Parasocial Relationships with YouTubers {#sec-h4}

```{r}
#| label: yt-anova

# anova of mean malleability scores 
anov1 <- aov(malleable_score ~ yt_match_all, data = favorite_youtuber)
anov1_hsd <- TukeyHSD(anov1)

anovp <- aov(composite ~ yt_match_all, data = favorite_youtuber)
```

@@

```{r}
#| label: tukey-hsd-report-function

report_tukey <- function(tukey_object, comparison, digits = 2, p_digits = 3) {
  factor_name <- names(tukey_object)[1]
  results <- tukey_object[[factor_name]]

  if (!comparison %in% rownames(results)) {
    stop(glue::glue("Comparison '{comparison}' not found in TukeyHSD object."))
  }

  diff <- round(results[comparison, "diff"], digits)
  lwr <- round(results[comparison, "lwr"], digits)
  upr <- round(results[comparison, "upr"], digits)
  pval <- results[comparison, "p adj"]

  p_string <- if (pval < 0.001) {
    "p < .001"
  } else {
    paste0("p = ", format(round(pval, p_digits), nsmall = p_digits))
  }

  glue::glue(
    "{comparison}: M difference = {diff}, 95% CI [{lwr}, {upr}], {p_string}."
  )
}
```

I hypothesized that having a parasocial relationship with a YouTuber of a race other than one's own would moderate the relationship between the amount of time children spent on YouTube and their racial attitudes. In the present sample, `r as.character(sum(favorite_youtuber$yt_match_all == "Match"))` children's favorite YouTubers were of a matching race/ethnicity (Match) and `r as.character(sum(favorite_youtuber$yt_match_all == "Mismatch"))` were of a different race/ethnicity (Mismatch). `r as.character(sum(favorite_youtuber$yt_match_all == "None"))` children did not specify an identifiable favorite YouTuber (None). YouTuber race/ethnicity was coded using publicly available online information, and children's race/ethnicity was reported by parents. To test a potential relationship between parasociality, race and ethnicity, and racial attitudes, I first conducted an ANOVA so as to assess whether there were significant differences in racial attitudes between favorite YouTuber types. This test revealed that there were significant differences in racial attitudes across favorite YouTuber groups (`r as.character(report_anova(anov1))`). A post-hoc Tukey's HSD test showed that racial attitudes in the Mismatch group were significantly different than those of children in the Match group (`r as.character(report_tukey(anov1_hsd, "Mismatch-Match"))`). No significant differences were observed between Mismatch and None (`r as.character(report_tukey(anov1_hsd, "None-Mismatch"))`), nor between Match and None (`r as.character(report_tukey(anov1_hsd, "None-Match"))`). As such, children with a YouTuber whose race/ethnicity matched their own expressed more fixed racial attitudes than those whose favorite YouTuber was of a race/ethnicity other than their own.

```{r}
#| label: parasocial-regressions

# Effect of YouTuber race match and parasocial relationship on malleability (uncentered)
lmp <- lm(malleable_score ~ yt_match_all * composite + regularity_score, data = favorite_youtuber)

# Effect of YouTuber race match and parasocial relationship on malleability (centered)
lmp_centered <- lm(malleable_score ~ yt_match_all * composite_centered + regularity_centered + Ptime_max_score * composite_centered, data = favorite_youtuber)
```
